Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-08-15 TEX/draft_biology.tex
Revised Appendix C. Several open questions remained

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\tamir}{x}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\RPP}{\mathbb{R}^{P\times P}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\hx}{\hat{x}} 
\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}

@@

In the presence of noise, we get additional bias terms denoted by $b_p$ in~\eqref{eq:ac_micrographs}. The mean ($p=1$) is unbiased  since the noise is assumed to have zero mean. For the second-order autocorrelation ($p=2$), we have
\[\begin{aligned} 
a^2_\II[\Bell] &=
\frac{1}{N^2}\sum_{\mb i }\II[\mb i]\II[\mb
i+\Bell]\\
&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell]. 
\end{aligned}\]
The first term is given by~\eqref{eq:general_moment} for $p=2$. 
The cross terms vanish in the limit. 
%Considering the terms one-by-one, the first term is independent of the
%noise, and as shown above converges to $\gamma \langle
%m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
%satisfies
%\[\begin{aligned} 
%\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\Bell]\varepsilon[\mb i + \Bell] &=
%\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
%i)\varepsilon_{\omega_j}[\mb i + \Bell]\\
%&\to \gamma\mathbb{E}_{\omega,\varepsilon}[I_{\omega}\varepsilon]\\ 
%&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\varepsilon}[\varepsilon] = 0, \end{aligned}\]
%where $\varepsilon_{\omega_j}[\Bell] = \varepsilon(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\varepsilon$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$. A similar argument applied to the third term shows that it
%also vanishes as $N\to\infty$. 
The fourth term is zero unless $\Bell=0$, in which case it converges to $\sigma^2$.
% $\Bell \neq \mb{0}$ %then since the noise is zero mean and
%i.i.d. this term vanishes. If $\Bell = \mb0$ then
%\[ \frac{1}{N^2}\sum_{i,j=1}^m\varepsilon[\Bell]^2 \to \sigma^2.\]
Thus, we conclude
\[ a^2_\II[\Bell] \to \gamma\langle a^2_{I_{\omega}}[\Bell]\rangle_{\omega} + \sigma^2\delta[\Bell],\]
where the  bias term $b_2[\Bell] = \sigma^2\delta[\Bell]$   depends only on the variance of the noise $\sigma^2$.

For the third moments, we get 8 terms:
\[\begin{aligned} 
&a^3_\II[\Bell_1, \Bell_2] =
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(3)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(4)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(5)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(6)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(7)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
	\item  Term (1) is treated by~\eqref{eq:general_moment} for $p=3$;
	\item Term (2) is the third-order autocorrelation of  pure noise  which vanishes in the limit; 
	\item Terms (3)-(5) depend linearly on the noise and hence
	vanish in the limit;
	\item For term (6), if $\Bell_1\neq \Bell_2$ the term
	vanishes in the limit. If $\Bell_1 = \Bell_2$ then
	\[ \begin{aligned}
        \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
      &= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
      \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
      %&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
      %&= \gamma\sigma^2Lm_1[\phi],
    \end{aligned}\]
	where $\langle a^1_{I_{\omega}}\rangle_{\omega}$ is the mean of the volume. 
	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
	%That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
%	\item For term (7), if $\Bell \neq \mb 0$ then once again
%	this term vanishes, whereas if $\Bell_2 = \mb 0$ then it becomes
%	\[ \frac{1}{N^2}\sum_{\mb i}\varepsilon[\Bell]^2\widetilde\II(\mb i + \Delta\mb
%	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
%		i}\varepsilon_{\omega}[\Bell]^2I_{\omega}(\mb i + \Bell_2) \to
%	\gamma\sigma^2Lm_1[\phi].\]
	%Similarly, terms (7) (8) vanishes if $\Bell_2\neq \mb 0$ and
	%converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
\end{itemize}
%Similarly, terms (7) (8) contributes $\delta$ functions similar to (6).
Thus, we conclude that
\[ a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
\delta[\Bell_1] + \delta[\Bell_2]\Big),\]
where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
Note that $\gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$ is approximately the mean of the micrograph since  $a^1_\II \approx a^1_{\tilde\II} \approx \gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$. Therefore, we do not need prior knowledge of $\gamma$ to effectively
debias the third-order autocorrelation.

@@

For $\Bell \in [-(P-1), P-1]^2$, let us define 
\[\begin{aligned} 
\mathfrak{a}^2[k, q] & =
\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{aligned}\]
where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
\begin{align}
 a^2_\II[\Bell] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
 \label{eq:approxprolatesdiscrete}
\end{align}
This holds because the continuous PSWFs form an orthogonal basis, and their discretized counterparts are (empirically) almost orthogonal. As a result, for our purposes, the pair of equations above provides a basis expansion for the autocorrelations.

@@

Crucially, following this formalism, it is now straightforward to account for all in-plane rotations and reflections of the micrograph. Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation: this is why this the PSWF basis is called \emph{steerable}~\cite{landa2017steerable,zhao2016fast}. By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
\[ \II^{\alpha,+}[\mb i+\Bell] \approx \sum_{k,q}a_{k,q}e^{-\iota k\alpha}\psi_{k,q}[\Bell],\]
and the reflection followed by a rotation by angle $\alpha$:
\[ \II^{\alpha,-}[\mb i+\Bell] \approx \sum_{k,q}\overline{a_{k,q}}e^{-\iota k\alpha}\psi_{k,q}[\Bell].\]
%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
\[\begin{aligned} 
\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k,q}[\mb i] +
\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\\ 
&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], \end{aligned}\]
where in the last equality we used that $a_{0,q}[\mb i]$ is real since both $\II$ and $\psi_{0,q}$ are real valued (more generally, $a_{-k,q}=\overline{a_{k,q}}$).
Thus, the second-order autocorrelation, though two-dimensional, effectively only provides radial information.

@@

We now turn out attention to the third order autocorrelation. Following the same lines, we define the coefficients:
\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
\end{aligned}\]
where the patch expansion coefficients $a_{k,q}$ are as defined in~\eqref{eq:patchcoefficients}.
The coefficients $\mathfrak{a}^3[k_1,q_1;k_2,q_2]$ are related to the third-order autocorrelation via the approximate identity:
\[ a^3_\II[\Bell_1, \Bell_2] \approx \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{a}^3[k_1,q_1;k_2,q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.\]
Averaging over all rotations of $\II$ and its reflection, we obtain
\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right),\\
&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}.\end{aligned}\]
Thus, similarly to the second-order autocorrelation, averaging over all in-plane rotations reveals that the 4-D third-order autocorrelation truly only carries information along three dimensions.

@@

\TODO{===}

\be\label{eq:PSWF_defn_eq}
\alpha_{k,q}\psi_{k,q}(\mb k) = \sum_{\mb i}\psi_{k,q}(\mb i)e^{-2\pi \iota (\mb i\cdot\mb k)}
\ee

\TODO{===}

We derive a relation between the steered bispectrum derived in Sect.~\ref{sec:steering} to the volume, expanded in a suitable basis. Specifically, expand the Fourier-transformed volume as
\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
where $k=||\kk||_2$, $c$ is the assumed bandlimit, $Y_{\ell}^m$ is the complex spherical harmonics
\[ Y_{\ell,m}(\theta,\varphi) = \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]

where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase, and $j_{\ell,s}$ are normalized spherical Bessel functions given by
\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
where $j_{\ell}$ is the spherical Bessel function of order $\ell$, $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$, and the radius satisfies $k\in[0,1/2]$ in Fourier space since $1/2$ is the Nyquist frequency [ISBI].

Then
\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}a_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta},\]
whenever $k\leq 1$. Express this in 2D PSWFs so \TODO{Eitan: I stopped here}
\[ \widehat I_{\omega}(ck,\theta) = \sum_{N,n}b_{N,n}\psi_{N,n}(k,\theta),\]
where in papers the 2D PSWFs are defined as
\[ \psi_{N,n}(k,\theta) = \frac{1}{\sqrt{2\pi}}R_{N,n}(k)e^{ik\theta},\]
but in Boris' code the expansion is actually performed with respect to
\[ \widetilde\psi_{N,n}(k,\theta) = \frac{1}{2\sqrt{2\pi}}\alpha_{N,n}R_{N,n}(k)e^{ik\theta},\]
where $\alpha_{N,n}$ are the eigenvalues associated with $\psi_{N,n}$ - see Sect.~\ref{sec:PSWFs_props} below.

We then get
\[\begin{aligned} b_{N,n} &= \frac{1}{\sqrt{2\pi}}\int_0^{2\pi}\int_0^1\widehat I_{\omega}(ck,\theta)R_{N,n}(k)e^{-iN\theta}k\, dk\, d\theta,\\
&= \sum_{\ell,m,m',s}a_{\ell,m,s}[\sqrt{2\pi}Y_{\ell,m'}(\pi/2,0)]D_{m',m}^{\ell}(\omega)\left(\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk\right)\left(\frac{1}{2\pi}\int_0^{2\pi}e^{i(m'-N)\theta}\, d\theta\right),\\
&= \sum_{\ell\geq |N|}\sum_{m,s}a_{\ell,m,s}D_{N,m}^{\ell}(\omega)\beta_{\ell,s;N,n},\end{aligned}\]
where
\[ \beta_{\ell,s;N,n} = \left\{\begin{array}{ll} \sqrt{2\pi}Y_{\ell,N}(\pi/2,0)\int_0^1j_{\ell,s}(k)R_{N,n}(k)k\, dk, & \ell\geq |N|,\\ 0, & \ell<|N|\end{array}\right.,\]
can be precomputed.

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\RL}{\mathbb{R}^L}
\newcommand{\tamir}{x}
\newcommand{\CL}{\mathbb{C}^L}
\newcommand{\RN}{\mathbb{R}^N}
\newcommand{\RNN}{\mathbb{R}^{N\times N}}
\newcommand{\RPP}{\mathbb{R}^{P\times P}}
\newcommand{\CNN}{\mathbb{C}^{N\times N}}
\newcommand{\inner}[1]{\left\langle {#1} \right\rangle}
\newcommand{\hx}{\hat{x}} 
\newcommand{\one}{\mathbf{1}} 
\newcommand{\SNR}{\ensuremath{\textsf{SNR}}}
\newcommand{\be}
{\begin{equation}}
\newcommand{\ee}
{\end{equation}}

@@

In the presence of noise, we get additional bias terms denoted by $b_p$ in~\eqref{eq:ac_micrographs}. The mean ($p=1$) is unbiased  since the noise is assumed to have zero mean. For the second-order autocorrelation ($p=2$), we have
\[\begin{aligned} 
a^2_\II[\Bell] &=
\frac{1}{N^2}\sum_{\mb i }\II[\mb i]\II[\mb
i+\Bell]\\
&= \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell] + \frac{1}{N^2}\sum_{\mb i }\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]\\ &+ \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\widetilde\II[\mb i + \Bell] + \frac{1}{N^2}\sum_{\mb i }\varepsilon[\mb i]\varepsilon[\mb i + \Bell]. 
\end{aligned}\]
The first term is given by~\eqref{eq:general_moment} for $p=2$. 
The cross terms vanish in the limit. 
%Considering the terms one-by-one, the first term is independent of the
%noise, and as shown above converges to $\gamma \langle
%m_2[I_{\omega}]\rangle_{\omega}$ as $N\to\infty$. The second term
%satisfies
%\[\begin{aligned} 
%\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\Bell]\varepsilon[\mb i + \Bell] &=
%\frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{j, \mb i}I_{\omega_j}(\mb
%i)\varepsilon_{\omega_j}[\mb i + \Bell]\\
%&\to \gamma\mathbb{E}_{\omega,\varepsilon}[I_{\omega}\varepsilon]\\ 
%&= \gamma \mathbb{E}_{\omega}[I_{\omega}]\mathbb{E}_{\varepsilon}[\varepsilon] = 0, \end{aligned}\]
%where $\varepsilon_{\omega_j}[\Bell] = \varepsilon(\mb i + \mb s_j)$ and we used the fact that the orientations $\omega$ and the noise $\varepsilon$ are independent, and $\mathbb{E}_{\omega}[I_{\omega}] = \langle m_1[I_{\omega}]\rangle_{\omega}$. A similar argument applied to the third term shows that it
%also vanishes as $N\to\infty$. 
The fourth term is zero unless $\Bell=0$, in which case it converges to $\sigma^2$.
% $\Bell \neq \mb{0}$ %then since the noise is zero mean and
%i.i.d. this term vanishes. If $\Bell = \mb0$ then
%\[ \frac{1}{N^2}\sum_{i,j=1}^m\varepsilon[\Bell]^2 \to \sigma^2.\]
Thus, we conclude
\begin{equation} \label{eq:second_order_ac_volume_data}
a^2_\II[\Bell] \to \gamma\langle a^2_{I_{\omega}}[\Bell]\rangle_{\omega} + \sigma^2\delta[\Bell],
\end{equation}
where the  bias term $b_2[\Bell] = \sigma^2\delta[\Bell]$   depends only on the variance of the noise $\sigma^2$.

For the third moments, we get 8 terms:
\[\begin{aligned} 
&a^3_\II[\Bell_1, \Bell_2] =
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(3)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(4)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(5)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(6)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(7)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
	\item  Term (1) is treated by~\eqref{eq:general_moment} for $p=3$;
	\item Term (2) is the third-order autocorrelation of  pure noise  which vanishes in the limit; 
	\item Terms (3)-(5) depend linearly on the noise and hence
	vanish in the limit;
	\item For term (6), if $\Bell_1\neq \Bell_2$ the term
	vanishes in the limit. If $\Bell_1 = \Bell_2$ then
	\[ \begin{aligned}
        \frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
      &= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
      \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
      %&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
      %&= \gamma\sigma^2Lm_1[\phi],
    \end{aligned}\]
	where $\langle a^1_{I_{\omega}}\rangle_{\omega}$ is the mean of the volume. 
	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
	%That is because by the Fourier projection-slice theorem, the Fourier transform of the projections correspond to the restriction of the 3D Fourier transform of the volume to a slice passing through the origin, so in particular the DC components of each projection and the volume are identical, so $\sum_{i,j,k}V(i,j,k) = \sum_{i,j}I_{\omega}(i,j)$.
%	\item For term (7), if $\Bell \neq \mb 0$ then once again
%	this term vanishes, whereas if $\Bell_2 = \mb 0$ then it becomes
%	\[ \frac{1}{N^2}\sum_{\mb i}\varepsilon[\Bell]^2\widetilde\II(\mb i + \Delta\mb
%	i_2) = \frac{NL^2}{M^2}\cdot\frac{1}{NL^2}\sum_{\omega,\mb
%		i}\varepsilon_{\omega}[\Bell]^2I_{\omega}(\mb i + \Bell_2) \to
%	\gamma\sigma^2Lm_1[\phi].\]
	%Similarly, terms (7) (8) vanishes if $\Bell_2\neq \mb 0$ and
	%converges to $\gamma\sigma^2Lm_1[\phi]$ otherwise.
\end{itemize}
%Similarly, terms (7) (8) contributes $\delta$ functions similar to (6).
Thus, we conclude that
\begin{equation} \label{eq:third_order_ac_micro_volume}
a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
\delta[\Bell_1] + \delta[\Bell_2]\Big),
\end{equation}
where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
Note that $\gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$ is approximately the mean of the micrograph since  $a^1_\II \approx a^1_{\tilde\II} \approx \gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$. Therefore, we do not need prior knowledge of $\gamma$ to effectively
debias the third-order autocorrelation.

@@

For $\Bell \in [-(P-1), P-1]^2$, let us define 
\begin{equation} \label{eq:PSWF_expansion}
\mathfrak{a}^2[k, q]  =
\sum_{\Bell}a^2_\II[\Bell]\overline{\psi_{k,q}[\Bell]}, \end{equation}
where $\psi_{k,q}[\Bell] := \psi_{k,q}(\Bell/(P-1))$ is a discretization of the PSWFs. \TODO{Range of $k,q$? need approx orthonormality in discrete...}
Knowledge of these coefficients is essentially equivalent to knowledge of the second-order correlations owing to the following approximate identity:
\begin{align}
 a^2_\II[\Bell] & \approx \sum_{k,q}\mathfrak{a}^2[k,q]\psi_{k,q}[\Bell].
 \label{eq:approxprolatesdiscrete}
\end{align}
This holds because the continuous PSWFs form an orthogonal basis, and their discretized counterparts are (empirically) almost orthogonal. As a result, for our purposes, the pair of equations above provides a basis expansion for the autocorrelations.

@@

Crucially, following this formalism, it is now straightforward to account for all in-plane rotations and reflections of the micrograph. Indeed, as can be seen from the definition of the (continuous) PSWFs~\eqref{eq:prolatesdef}, the effects of rotations and reflections on expansion coefficients of real images are, respectively, phase modulation and conjugation: this is why this the PSWF basis is called \emph{steerable}~\cite{landa2017steerable,zhao2016fast}. By analogy in the discrete case, we have the following approximate expansions for a patch rotated about its center $\mb i$ by an angle $\alpha$:
\[ \II^{\alpha,+}[\mb i+\Bell] \approx \sum_{k,q}a_{k,q}e^{-\iota k\alpha}\psi_{k,q}[\Bell],\]
and the reflection followed by a rotation by angle $\alpha$:
\[ \II^{\alpha,-}[\mb i+\Bell] \approx \sum_{k,q}\overline{a_{k,q}}e^{-\iota k\alpha}\psi_{k,q}[\Bell].\]
%where we used the fact that for real-valued images we have $a_{-k,q}=\overline{a_{k,q}}$ for both PSWFs and FB.
Averaging over all rotations of the patch $\II(\mb i + \Delta\mb i)$ and its reflection we get
\begin{align} \label{eq:second_order_ac_pswf}
\mathfrak{a}^2[k,q] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k,q}[\mb i] +
\overline{a_{k,q}}[\mb i]\right)e^{-\iota k\alpha}\, d\alpha\right)\nonumber\\ 
&= \delta[k] \frac{1}{N^2}\sum_{\mb i}\II[\mb i]a_{0,q}[\mb i], 
\end{align}
where in the last equality we used that $a_{0,q}[\mb i]$ is real since both $\II$ and $\psi_{0,q}$ are real valued (more generally, $a_{-k,q}=\overline{a_{k,q}}$).
Thus, the second-order autocorrelation, though two-dimensional, effectively only provides radial information.

@@

We now turn out attention to the third order autocorrelation. Following the same lines, we define the coefficients:
\[\begin{aligned} \mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \sum_{\Bell_1, \Bell_2} a^3_\II[\Bell_1,\Bell_2]\overline{\psi_{k_1,q_1}[\Bell_1]}\psi_{k_2,q_2}[\Bell_2]\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\sum_{\Bell_1}\II[\mb i+\Bell_1]\overline{\psi_{k_1,q_1}[\Bell_1]}\right)\left(\sum_{\Bell_2}\II[\mb i+\Bell_2]\psi_{k_2,q_2}[\Bell_2]\right)\\
&= \frac{1}{N^2}\sum_{\mb i}\II[\mb i] a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]},
\end{aligned}\]
where the patch expansion coefficients $a_{k,q}$ are as defined in~\eqref{eq:patchcoefficients}.
The coefficients $\mathfrak{a}^3[k_1,q_1;k_2,q_2]$ are related to the third-order autocorrelation via the approximate identity:
\[ a^3_\II[\Bell_1, \Bell_2] \approx \sum_{\substack{k_1,q_1\\ k_2,q_2}}\mathfrak{a}^3[k_1,q_1;k_2,q_2]\psi_{k_1,q_1}[\Bell_1]\overline{\psi_{k_2,q_2}[\Bell_2]}.\]
Averaging over all rotations of $\II$ and its reflection, we obtain
\begin{align} \label{eq:third_order_ac_pswf}
\mathfrak{a}^3[k_1,q_1;k_2,q_2] &= \frac{1}{N^2}\sum_{\mb i}\II[\mb i]\left(\frac{1}{4\pi}\int_0^{2\pi}\left(a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]} + \overline{a_{k_1,q_1}[\mb i]}a_{k_2,q_2}[\mb i]\right)e^{-\iota(k_1-k_2)\alpha}d\alpha\right), \nonumber\\
&= \delta[k_1 - k_2]\frac{1}{N^2}\sum_{\mb i}\II[\mb i]\Re\{a_{k_1,q_1}[\mb i]\overline{a_{k_2,q_2}[\mb i]}\}. 
\end{align}
Thus, similarly to the second-order autocorrelation, averaging over all in-plane rotations reveals that the 4-D third-order autocorrelation truly only carries information along three dimensions.

@@

Until now, we have established  simple relations between the autocorrelations of the micrographs and the autocorrelations of the volume. Now, we complete the picture by deriving the connection with the volume itself.

We start by some preliminary computations. Let us  expand the Fourier transform of the volume as
\begin{equation} \label{eq:volume_expansion_app} 
\widehat \phi(ck, \theta, \varphi) = \sum_{\ell = 0}^L\sum_{m=-\ell}^{\ell}\sum_{s=1}^{S(\ell)}\tamir_{\ell, m, s}Y_{\ell}^m(\theta,\varphi)j_{\ell,s}(k), \quad k\leq 1,
\end{equation}
%\[ \widehat \phi(c\kk) = \sum_{\ell,m,s}a_{\ell,m,s}j_{\ell,s}(k)Y_{\ell,m}(\kk/k),\quad k\leq 1,\]
%where $k=||\kk||_2$, 
\TODO{How do we choose $S(\ell)$?}where $c$ is the bandlimit, $j_{\ell,s}$ is the normalized spherical Bessel functions given by
\[ j_{\ell, s}(k) = \frac{4}{|j_{\ell+1}(u_{\ell, s})|}j_{\ell}(2u_{\ell,s} k),\]
$j_{\ell}$ is the spherical Bessel function of order $\ell$ and  $u_{\ell,s}$ is the $s$th positive zero of $j_{\ell}$. We use 
the complex spherical harmonics $Y_{\ell}^m$ defined by  
\[ Y_{\ell,m}(\theta,\varphi) := \sqrt{\frac{2\ell+1}{4\pi}\cdot\frac{(\ell-m)!}{(\ell+m)!}}P_{\ell}^m(\cos\theta)e^{i m\varphi},\]
where $P_{\ell}^m$ are the associated Legendre polynomials with the Condon-Shortley phase. 
Sampling at the Nyquist-rate dictates $k\in[0,1/2]$~\cite{levin20173d}. \TODO{Didn't we say that $k\leq 1$?} With this notation, 
the Fourier transform of a  projection taken from the viewing direction $\omega\in SO(3)$ can be written as 
\[ \widehat I_{\omega}(ck,\theta) = \sum_{\ell,m,m',s}\tamir_{\ell,m,s}Y_{\ell,m'}(\pi/2,0)D_{m',m}^{\ell}(\omega)j_{\ell,s}(k)e^{im'\theta}.\]
%whenever $k\leq 1$. 
%where $D_{m',m}^{\ell}$ is the Wigner D-matrix.
